Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-11-07 batchdedup/scheduling.tex
fixed round variable to k in scheduling algorithms

From our requirements a model that closely fits our goals is the dual version
of the
bin packing problem. In standard bin packing the goal is to fit all of the
items into as few bins as possible, without overfilling any bins. In the dual
version of the problem however as many bins as possible are to filled to at
least some minimum level. This fits our purpose because we want to maximize the
number of rounds to minimize VM backup times, with some constraint to keep the
efficiency benefits of batch processing and keep the total backup time low.
In our dual-bin-packing solution the constraint is to keep the total
cost of the schedule under a time limit rather than mandating a minimum bin
level. We have adapted
an algorithm for dual bin packing\cite{DualBinPacking} to fit our VM
scheduling problem. The algorithm adapted is called iterated A and works by
iteratively callng a bin packing heuristic A with the items to be scheduled and
the number of bins, using binary search to arrive at the best number of
bins. A(I,N) is defined to return the optimality of packing set I into N bins
using A. We take this basic idea and look at several VM packing heuristics to
arrive at an efficient packing algorithm. More formally, our adaptation of the
iterated A algorithm is defined as:

%lstset{basicstyle=\ttfamily\tiny
%}
\todo{justify choice of initial UB (right now it is mostly arbitrary)}
\begin{figure}
\begin{lstlisting}[frame=single]
Iterated A:
Set UB=min(n,2*v)
Set LB=1
while UB>LB
  set N = (UB+LB+1)/2
  if A(machines,N) > T, set UB=N-1
  else set LB=N
Halt
\end{lstlisting}
\caption{Iterated A scheduling algorithm, requires good choice of A to be effective}
\end{figure}

where A(machines,N) returns the total backup time of the schedule for N rounds\\
This algorithm returns the packing generated by A(machines,UB) after loop finishes

>>>>

From our requirements a model that closely fits our goals is the dual version
of the
bin packing problem. In standard bin packing the goal is to fit all of the
items into as few bins as possible, without overfilling any bins. In the dual
version of the problem however as many bins as possible are to filled to at
least some minimum level. This fits our purpose because we want to maximize the
number of rounds to minimize VM backup times, with some constraint to keep the
efficiency benefits of batch processing and keep the total backup time low.
In our dual-bin-packing solution the constraint is to keep the total
cost of the schedule under a time limit rather than mandating a minimum bin
level. We have adapted
an algorithm for dual bin packing\cite{DualBinPacking} to fit our VM
scheduling problem. The algorithm adapted is called iterated A and works by
iteratively callng a bin packing heuristic A with the items to be scheduled and
the number of bins, using binary search to arrive at the best number of
bins. A(I,k) is defined to return the optimality of packing set I into k bins
using A. We take this basic idea and look at several VM packing heuristics to
arrive at an efficient packing algorithm. More formally, our adaptation of the
iterated A algorithm is defined as:

%lstset{basicstyle=\ttfamily\tiny
%}
\todo{justify choice of initial UB (right now it is mostly arbitrary)}
\begin{figure}
\begin{lstlisting}[frame=single]
Iterated A:
Set UB=min(n,2*v)
Set LB=1
while UB>LB
  set k = (UB+LB+1)/2
  if A(machines,k) > T, set UB=k-1
  else set LB=k
Halt
\end{lstlisting}
\caption{Iterated A scheduling algorithm, requires good choice of A to be effective}
\end{figure}

where A(machines,k) returns the total backup time of the schedule for k rounds\\
This algorithm returns the packing generated by A(machines,UB) after loop finishes
